\documentclass[a4paper,10pt]{article} % Default font size and paper size
    \usepackage{tgpagella}
    \usepackage[T1]{fontenc}
    \usepackage{enumitem}
    \usepackage{hyperref}
    \usepackage{array}
    \usepackage{fontawesome}
    \usepackage{parskip, url}
    \usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors
    \usepackage[big]{layaureo}
    \usepackage{hyperref} % Required for adding links	and customizing them
    \definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
    \hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document
    \usepackage{titlesec} % Used to customize the \section command
    \titleformat{\section}{\Large\bfseries\raggedright}{}{0em}{} 
    \titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections
    \newcommand{\seticon}[1]{{\csname #1\endcsname}}
    
    \begin{document}
    \pagestyle{empty} % Removes page numbering
    {\centering
    \par{\Huge Xinyue {Liu}}\par % Your name
    \vspace{0.5em}
    \centering{
         \seticon{faPhone} +1-508-873-4348 $|$ 
         \seticon{faEnvelope} \href{mailto:xliu4@wpi.edu}{xliu4@wpi.edu} $|$ 
         \seticon{faChain}     \url{http://cinv.ro}
         \par}}
    \vspace{0.5em}
    
    \section{Objective}
    I am looking for a research scientist or applied scientist position in AI-related fields.
    
    \section{Education}
    \begin{tabular}{ll}	
    \textbf{2018} & \textbf{Worcester Polytechnic Institute}\\ 
    \footnotesize{(expected)}& \emph{Ph.D. in Computer Science}   \\
    \textbf{2013} & \textbf{Hong Kong University of Science \&. Technology} \\
    &\emph{M.Sc. in Information Technology}  \\ 
     \textbf{2012}& \textbf{University of Electronic Science \&. Technology of China}   \\
    &\emph{B.Eng. in Software Engineering}  
    %\textsc{Spring} 2011 & Exchanged at University of California, Santa Barbara, USA\\
    %\textsc{Summer} 2011 & Exchanged at University of California, Los Angeles, USA\\
    \end{tabular}
    
    \section{Employment}
    \begin{tabular}{p{10cm}r}
    \textbf{IBM T. J. Watson Research Center} & \textbf{Yorktown Heights, NY}\\ 
    \emph{Research Intern} & {Summer 2018} \\
    \textbf{Worcester Polytechnic Institute} & \textbf{Worcester, MA}\\
    \emph{Research Assistant} & \textsc{2014 - 2018} \\ 
    \textbf{Hong Kong University of Science \&. Technology} & \textbf{Hong Kong}  \\
    \emph{Research Assistant} & \textsc{2013 - 2014} 
    \end{tabular}
    
    
    \section{Research Interests}
    \begin{itemize}
    \item[$\circ$] Deep Learning:
    \ref{treegan}
    \ref{tree2text}
    \ref{net2text}
    \ref{mmr}
    \ref{rAE}
    \ref{DROM}
    \vspace{-0.25em}
    \item[$\circ$] Recommender Systems:
    \ref{kdd18}
    \ref{icdm17a}
    \ref{icdm17b}
    \ref{sdm16}
    \ref{rAE}
    \vspace{-0.25em}
    \item[$\circ$] Graph Mining: 
    \ref{treegan}
    \ref{kdd18}
    \ref{ijcnn17}
    \ref{sdm17a}
    \ref{sdm17b} 
    \ref{cikm16} 
    \ref{COM}
    \ref{MAGL} 
    \vspace{-0.25em}
    \item[$\circ$] Biological Signals Analysis \& Mining:
    \ref{CGL}
    \ref{ijcnn17}
    \ref{sdm17a}
    \ref{MGGL} 
    \ref{DROM}
    \ref{MAGL}
    \end{itemize}
    
    \section{Publication}
    \begin{enumerate}[label=(C\arabic*).]
        {\item \label{treegan} 
        \textbf{{Xinyue Liu}}, Xiangnan Kong, Lei Liu, Kuorong Chiang. 
        \href{https://arxiv.org/abs/1808.07582}{
        ``Syntax-aware Sequence Generation with Generative Adversarial Networks''},
        \emph{IEEE International Conference on Data Mining (ICDM '18)}, November 2018.
        }
        
        {\item \label{CGL}
        Hang Yin, \textbf{{Xinyue Liu}}, Xiangnan Kong. 
        ``Coherent Graphical Lasso for Brain Network Discovery '', 
        \emph{IEEE International Conference on Data Mining (ICDM '18)}, November 2018.
        }
        
        \item \label{kdd18} 
        \textbf{{Xinyue Liu}}, Xiangnan Kong, Philip S. Yu. 
        \href{http://cinv.ro/files/KDD18.pdf}
        {``Active Opinion Maximization on Social Networks"}, 
        \emph{ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD '18)}, August 2018.
                            
        \item \label{icdm17a} 
        \textbf{{Xinyue Liu}}, Yuanfang Song, Charu Aggarwal, Yao Zhang, Xiangnan Kong. 
        \href{http://cinv.ro/files/ICDM17.pdf}
        {``Item Recommendation with Life Cycles"}, 
        \emph{IEEE International Conference on Data Mining (ICDM '17)}, November 2017.                 
        
        \item \label{icdm17b} 
        Saket Sathe, Charu Aggarwal, Xiangnan Kong and \textbf{{Xinyue Liu}}. 
         ``Kernel-Based Feature Extraction For Collaborative Filtering", 
         \emph{IEEE International Conference on Data Mining (ICDM '17)}, November 2017.
                              
        \item \label{ijcnn17} 
        \textbf{{Xinyue Liu}}, Xiangnan Kong and Philip S. Yu. 
         \href{http://cinv.ro/files/IJCNN17.pdf}
         {``Collective Discovery of Brain Networks with Unknown Groups"}, 
         \emph{International Joint Conference On Neural Networks (IJCNN '17)}, May 2017.
                                  
        \item \label{sdm17a} 
        \textbf{{Xinyue Liu}}, Xiangnan Kong and Ann B. Ragin. 
         \href{http://cinv.ro/files/SDM17.pdf}
         {``Unified and Contrasting Graphical Lasso for Brain Network Discovery"}, 
         \emph{SIAM International Conference on Data Mining (SDM '17)}, April 2017.
                             
        \item \label{sdm17b} 
        Yao Zhang, Yun Xiong, \textbf{{Xinyue Liu}}, Xiangnan Kong, Yangyong Zhu. 
         \href{http://cinv.ro/files/SDM17_Yao.pdf}
         {``Meta-Path Graphical Lasso for Learning Heterogeneous Connectivities"}, 
         \emph{SIAM International Conference on Data Mining (SDM '17)}, April 2017.
                             
        \item  \label{cikm16} 
        \textbf{{Xinyue Liu}}, Xiangnan Kong and Yanhua Li. 
         \href{http://cinv.ro/files/CIKM16.pdf}
         {``Collective Traffic Prediction with Partially Observed Traffic History using Location-Based Social Media"}, 
         \emph{ACM International Conference on Information and Knowledge Management (CIKM '16)}, November 2016.
                             
        \item  \label{sdm16}
        \textbf{{Xinyue Liu}}, Charu Aggarwal, Yu-Feng Li, Xiangnan Kong, Xinyuan Sun and Saket Sathe. 
         \href{http://cinv.ro/files/SDM16.pdf}
         {``Kernelized Matrix Factorization for Collaborative Filtering"}, 
         \emph{SIAM International Conference on Data Mining (SDM '16)}, April 2016.
    \end{enumerate}
    
    \section{Manuscripts}
    \begin{enumerate}[label=(M\arabic*)., resume]
        {\item \label{MGGL}
        Hang Yin, \textbf{{Xinyue Liu}}, Xiangnan Kong. 
        ``Mixture Gaussian Graphical Lasso for Brain Network Discovery '', 
        (submitted to SDM' 19)
        }
    
        {\item 
         \label{tree2text}
         Shaofeng Xu, Yun Xiong, \textbf{{Xinyue Liu}}, Xiangnan Kong, Yangyong Zhu.
         ``Translating Source Code to Text by Exploiting
         Abstract Syntax Tree''. (submitted to SDM '19)
         }
    
        {\item 
         \label{net2text}
         Shaofeng Xu, Yun Xiong, \textbf{{Xinyue Liu}}, Xiangnan Kong, Yangyong Zhu.
         ``Translating Bipartite Graph Links to Text''. (submitted to SDM '19)
         }
    
         {\item \label{mmr}
         Thanh Tran, \textbf{{Xinyue Liu}}, Kyumin Lee, Xiangnan Kong. 
         ``Deep Metric-based Memory Recommender''. 
         (submitted to AAAI '19)
         }
    
         {\item \label{rAE}
         \textbf{{Xinyue Liu}}, Charu Aggarwal, Saket Sathe, Udayan Khurana, Horst Samulowitz, Xiangnan Kong. 
         ``Deep Recurrent Autoencoder for Temporal Collaborative Filtering''.
         (submitted to WSDM '19)
         }
         
        {\item \label{COM} 
        Jianjun Luo, \textbf{{Xinyue Liu}}, Xiangnan Kong. 
        ``Competitive Opinion Maximization in Social Networks". 
        (submitted to WSDM '19)
        }
    
        {\item \label{DROM}
        Xin Dai, Xiangnan Kong, \textbf{{Xinyue Liu}}, Constance Moore. 
        ``Dual-Attention Recurrent Networks for Affine Registration of Neuroimaging Data''. 
        (submitted to AAAI '19)
        }
    
        {\item \label{MAGL}
        Yao Zhang, Yun Xiang, Xiangnan Kong, \textbf{{Xinyue Liu}}, Yangyong Zhu. 
        ``Multi-task Attributed Graphical Lasso''.
        (submitted to AAAI '19) 
        }
    \end{enumerate}
    
    \iffalse
    \section{Work-in-Progress}
    \begin{enumerate}[label=(P\arabic*)., resume]
        %{\item 
        % \label{attention}
        % \textbf{{Xinyue Liu}}, Xiangnan Kong.
        %  ``Recurrent Attention Recommender''. (Planed)
        % }
    
        {\item \label{aod}
         Mingrui Wei, \textbf{{Xinyue Liu}}, Xiangnan Kong, Elke A. Rundensteiner.
         ``Active Outlier Detection''. %(submitted to ICLR '19)
         }
    
        {\item \label{csg}
         \textbf{{Xinyue Liu}}, Xiangnan Kong, Lei Liu, Kuorong Chiang.
         ``Context-Sensitive Sequence GAN''. %(submitted to ICLR '19)
         }
    
        {\item 
         \label{ctom}
         Jianjun Luo, \textbf{{Xinyue Liu}}, Xiangnan Kong.
         ``Continuous Opinion Maximization''.
         }
    
        {\item 
         \label{pn}
         Yao Zhang, \textbf{{Xinyue Liu}}, Yun Xiong, Xiangnan Kong, Yangyong Zhu.
          ``Pointer Network for Opinion Maximization''.
         }
    \end{enumerate}
    \fi
    
    
    
    \section{Teaching}
    \begin{tabular}{rl}	
    \textsc{Feb.- May., 2015} & \textbf{CS2333: Algorithms}  \\
    & Graduated Teaching Assistant, Worcester Polytechnic Institute, USA\\
    \end{tabular}
    
    \section{Awards}
    \begin{tabular}{rl}
    \textsc{Jun.} 2018 & ACM KDD Travel Award \normalsize\\
    \textsc{Oct.} 2017 & WPI Graduate Student Travel Award \normalsize\\
    \textsc{Oct.} 2017 & IEEE ICDM Travel Award  \normalsize \\
    \textsc{Mar.} 2017 & IEEE/ACM IJCNN Travel Award \normalsize \\
    \textsc{Mar.} 2017 & WPI Graduate Student Travel Award \normalsize\\
    \textsc{Oct.} 2016 & WPI Graduate Student Travel Award \normalsize\\
    \textsc{Aug.} 2016 & ACM CIKM Travel Award \normalsize\\
    \textsc{May.} 2016 & SIAM SDM Travel Award \normalsize\\
    \end{tabular}
    
    \section{Service}
    \begin{tabular}{rl}	
    \textbf{Journal Reviewer} & TKDD  \\
    \textbf{External Reviewer} & TKDE, TIST, TPAMI, KDD ('15 - '18), ICML ('18), ICDM ('15,'17), \\
        & SDM ('17, '18), CIKM ('15 - '17), NIPS ('16 - '18), IJCAI ('15, '17),\\
        & AAAI ('17), AISTAT ('17, '18), ICDE ('17), ASONAM ('17),\\
        & BigData('18), PAKDD ('18) \\
    \textbf{Conference Volunteer} & SDM '16, ICDM' 17, KDD '18
    \end{tabular}
    
    \end{document}
    